Data-driven approaches to identifying knowledge gaps in marine invertebrate biodiversity

### 2017-05-30 manuscript.Rmd
add proportions of species with obis, idigbio, gbif records

These results suggest that even when considering species lists that have been curated and that represent possibly the most accurate knowledge for this geographic area, today we could only reconstruct these list at 50 to 70% completedness based on digitized information. It highlights that additional digitization is necessary but even more importantly additional collecting is needed to validate the occurences of the species included in these lists.

>>>>

These results suggest that even when considering species lists that have been curated and that represent possibly the most accurate knowledge for this geographic area, today we could only reconstruct these lists partially based on digitized information. For instance, based on OBIS data the list would be at `r format_output(summary_richness_per_db_gom$prop_obis_in_gom[summary_richness_per_db_gom$taxon_name == "Porifera"]*100)`% complete for sponges to `r format_output(summary_richness_per_db_gom$prop_obis_in_gom[summary_richness_per_db_gom$taxon_name == "Mollusca"]*100)`% for molluscs. However, these levels drop significantly if we consider species for which museum specimens are available from  `r format_output(summary_richness_per_db_gom$prop_idigbio_in_gom[summary_richness_per_db_gom$taxon_name == "Mollusca"]*100)`% for molluscs to `r format_output(summary_richness_per_db_gom$prop_idigbio_in_gom[summary_richness_per_db_gom$taxon_name == "Annelida"]*100)`% for annelids.
It highlights that additional digitization is necessary but even more importantly additional collecting is needed to validate the occurences of the species included in these lists.
